\documentclass[10pt,a4paper]{article}       
\usepackage[utf8]{inputenc}  
\usepackage{amsthm,amsmath,amssymb,amsfonts,bbm} 
\usepackage[danish]{babel} 
\usepackage{xfrac} 
\usepackage{graphicx}   
\usepackage{fancyhdr}	
\usepackage[margin=1.10in]{geometry} 
\pagestyle{fancy}
\newcommand{\us}[1]{\underset{=}{#1}} 
\newcommand{\ul}[1]{\underline{#1}} 
\lhead{Carpe Diem. Memento Mori. YOLO. You miss all of the shots you don't take.} 
\chead{}     
\rhead{\today} 
\parindent 0cm 
\linespread{1.1}
\begin{document} 
\section*{Regeln}
You have 25 minutes to submit answers. There are 11 questions and a correct answer is always a positive real number i.e. question $i$ has answer $\theta_i \in \mathbb{R}_+$ for $i = 1,2,\ldots,11$. Submissions are made in the form of an interval:
$$
[\text{Min}, \text{Max}]
$$
Note that both endpoints are included. Each team has 16 guesses hence multiple submissions for questions is possible altough the score, and hence the correctness of the guess, will always be based on the \textbf{latest} submission to the question.
Submissions can be made throughout the quiz. 
The team's score is given by the formula:
$$
\left( 10 + \sum_{\substack{i : \text{Min}_i \leq \theta_i \leq \text{Max}_i}} \left\lfloor \frac{\text{Max}_i}{\text{Min}_i} \right\rfloor \right) \cdot 2^{11 - \# \text{correct guesses} }
$$
Where $\lfloor \cdot \rfloor$ is the floor function.\\ \\
Hence, at the beginning of the quiz all teams have a score of
$(10 + 0)\cdot 2^{11-0} = 20480$ points. \\
When the time is up, the team with the \textbf{lowest} score wins.\\
When submitting an interval it must clearly state:\\ \\
$\bullet$ Team\\
$\bullet$ Question\\
$\bullet$ Interval. \\ \\
Using scientific notation is allowed but must follow the conventions of R e.g.:\\
100 = 1e2 \\
93.000 = 93e3 \\
1.010.000.000 = 101e7 \\
etc.

After submission the team (and everybody else) will be able to see whether the guess is correct or not and if so the value of the answer in the sum i.e. $\lfloor \text{Max}_i / \text{Min}_i \rfloor$ as well as the updated total score.

\newpage
\section*{Fragen}
\begin{enumerate}
  \item The width of the painting \textit{Guernica} by Pablo Picaso in cm.
  
  \item Casualties in the largest maratime disaster; The wartime sinking of the German Wilhelm Gustloff in January 1945 in World War II by a Soviet Navy submarine.

  \item Number of recently extinct mammals as classified by the International Union for Conservation of Nature (IUCN). Defined as any mammal that have become extinct since the year 1500 CE

  \item Number of people killed in a stampede 
 

\end{enumerate}
\end{document}
