\documentclass[12pt,a4paper]{article}       
\usepackage[utf8]{inputenc}  
\usepackage{amsthm,amsmath,amssymb,amsfonts,bbm} 
\usepackage[danish]{babel} 
\usepackage{xfrac} 
\usepackage{graphicx}   
\usepackage{fancyhdr}	
\usepackage[margin=1.10in]{geometry} 
\pagestyle{fancy}
\newcommand{\us}[1]{\underset{=}{#1}} 
\newcommand{\ul}[1]{\underline{#1}} 
\lhead{Bowling for cbind} 
\chead{}     
\rhead{\today} 
\parindent 0cm 
\linespread{1.1}
\begin{document} 
\section*{Regeln}
You have 25 minutes to submit answers. There are 11 questions and a correct answer is always a positive real number i.e. question $i$ has answer $\theta_i \in \mathbb{R}_+$ for $i = 1,2,\ldots,11$. Submissions are made in the form of an interval:
$$
[\text{Min}_i, \text{Max}_i]
$$
Note that both endpoints are included. Each team has 16 guesses hence multiple submissions for questions is possible altough the score, and hence the correctness of the guess, will always be based on the \textbf{latest} submission to the question.
Submissions can be made throughout the quiz. 
The team's score is given by the formula:
$$
\left( 10 + \sum_{\substack{i : \text{Min}_i \leq \theta_i \leq \text{Max}_i}} \left\lfloor \frac{\text{Max}_i}{\text{Min}_i} \right\rfloor \right) \cdot 2^{11 - \# \text{correct guesses} }
$$
Where $\lfloor \cdot \rfloor$ is the floor function.\\ \\
Hence, at the beginning of the quiz all teams have a score of
$(10 + 0)\cdot 2^{11-0} = 20480$ points. \\
When the time is up, the team with the \textbf{lowest} score wins.\\
When submitting an interval it must clearly state:\\ \\
$\bullet$ Team\\
$\bullet$ Question\\
$\bullet$ Interval. \\ \\
Using scientific notation is allowed but must follow the conventions of R e.g.:\\
100 = 1e2 \\
93.000 = 93e3 \\
1.010.000.000 = 101e7 \\
etc.

After submission the team (and everybody else) will be able to see whether the guess is correct or not and if so the value of the answer in the sum i.e. $\lfloor \text{Max}_i / \text{Min}_i \rfloor$ as well as the updated total score.

\newpage
\section*{Fragen}
\begin{enumerate}

\item Length in meters of the shortest land-border of Russia.

\item Number of digits in the number $2^{123}$

\item Casualties in the deadliest disaster in aviation history

\item Highest FIFA-ranking of the Faroe Islands national football team

\item According to Finnish Army documents, from the outbreak of the Winter War 30th November 1939 to 22nd of december, how many confirmed sniper kill did Finnish soldier Simo Häyhä (1905-2002), who was known as Belaja Smert in russian (The White Death) have?

\item Super Mario 64, released 1996 has sold more than 11 million copies, on 11th Nov 2021 a new speedrun record was made for completing the game perfectly i.e. 120 stars. What is this record in seconds? 

\item The danish party 'Valgfest med mexicansk tema' (party letter E) held their electionparty at Mexibar on Nørrebro, using last years 'Partistøtte for open bar. How many votes did the party receive in the 2021 Regionsrådsvalg?

 \item The width of the painting \textit{Guernica} by Pablo Picaso in cm.


 \item Number of recently extinct mammals as classified by the International Union for Conservation of Nature (IUCN). Defined as any mammal that have become extinct since the year 1500 CE

  \item Number of sub 1-year old per super 100-year old danish citizens pr november 2020.
  
  \item Size in square kilometer of the Navajo Nation; the largest Native American Reservation in the US.
  
  \item Let $M_G, M_S, M_B$ we the number of Gold, Silver, and Bronze medals awarded at the Summer Olympics in Rio de Janeiro in 2016. What is $\max_{i \neq j} \left\{ |M_i - M_j| \right\}$ ?
  
  \item Number of songs on Spotify with more than 2 billion streamings, as of Nov 2020.
  
  \item What is the lowest possible percentage of the popular vote needed to win the Electoral College, and thereby win the US Precidency.\\   Assuming only two candidates and that the number of votes cast in each state is proportional to the population size of said state.
  
  \item Number of days Karl Dönitz served as German head of state.
  
  \item Number of digits in $100!$
  
  \item Let $(X_n)_{n \in \mathbb{N}}$ be a discrete Markov Chain on statespace $S = \{1,2,3,4,5,6\}$ 
  with transition probabilites $\bold{p_{ik}} = \frac{1}{6}, \quad i,k \in S$.
  Let $X_0 = 2$ and define 
  $$\tau = \inf\left\{ n \geq \pi : X_n = 6 \right\}$$
  what is 
  $$ E \left[ \sum_{n = 0}^{\tau}X_n \right] $$
  
  
  
 

\end{enumerate}
\end{document}
